Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-13 paper/drafts_and_revisions/2019-01-14/reviewers-response.tex

\emph{Accepted and changed}: We are sorry for the confusion. In the
species level GLM, we lumped all species from different networks
together. We have modified the text in \lr{M-R2-one-lumped-model-a} and
\lr{M-R2-one-lumped-model-b} to make this clearer. We actually did test
for random effects in the model. We tested random effects that allowed
for a random intercept for the network (but also its site, and the study
it comes from). In all cases, the variance among groups was zero. This
means that likely there are no differences on the distribution of
control capacity between networks (or site and study) and therefore it
was not necessary to include random effects in the models presented in
the paper. We have corrected this omission and describe the random
effects in \lr{M-R2-random-effects}.

\begin{quote}
``How were the model sets derived? Were all possible sub-models compared
or was a step-wise approach used?''
\end{quote}

\emph{Accepted and changed}: We actually compared all possible candidate
models. We have edited the manuscript on \lr{M-R2-all-candidates} to
include this information.

\begin{quote}
``Reciprocal links were included in the directed graph when dij = dji.
Would it have any effect if there was a little wiggle room there, e.g.,
when the two are close but not equal?''
\end{quote}

We did not actually evaluate this When we evaluate the impact of this on
our results. However, given that the interaction only a very small
fraction of interactions had a small asymmetry (see Figure R1) we don't
expect results to change considerably even when we include reciprocal
links when the asymmetry is small but not zero.

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/reviewers-response_files/figure-latex/fig-asymmetry-1.pdf}
\caption{\label{fig:fig-asymmetry}Histogram of the interaction asymmetries
between species. Previous research has shown that mutualistic
interactions are often highly asymmetric in natural communities. Only
16.5\% of interactions have asymetries smaller or equal than 0.5; 1\%
are smaller than 0.1.}
\end{figure}

\end{document}
